---
title: "`Thumbtrack::railsconf.today`"
output:
  github_document: {}
---
```{r config, include=FALSE}
library(knitr)
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,
               dev="png")
read_chunk("report.R")

library(tidyverse)
library(patchwork)

theme_set(theme_minimal(base_size=14))
```
```{r report, include=FALSE}
```

# How many people were using the site?

During the conference, the site was visited a total of
`r c_$during_conference_visits` times. Many of these visits were by the same
people. We know that the site was visited by `r c_$num_devices` unique devices,
but it is likely some of these devices are owned by the same people [^issue88].
Most of the visits were during conference hours. The hours of the conference,
along with the times of the conference events, are shown below.

[^issue88]: We are seeking to improve our Google Analytics integration. See [Issue #88](https://github.com/8thlight/thumbtrack/issues/88).

Key results:

* Visits were consistent across all three days of the conference.
* Low visits before the conference could indicate the need for better promotion.
* Low visits after conference hours could indicate the need to support Community Events.

```{r sessions, fig.width=8, fig.height=8}
sessions_per_hour_plot +
  { conference_day_type_plot + hour_type_plot } +
  plot_layout(nrow = 2)
```
