---
title: "`Thumbtrack::railsconf.today`"
output:
  github_document: {}
---
```{r config, include=FALSE}
library(knitr)
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,
               dev="png")
read_chunk("report.R")

library(tidyverse)
library(patchwork)

theme_set(theme_minimal(base_size=14))
```
```{r report, include=FALSE}
```

# How many people were using the site?

During the conference, the site was visited a total of
`r c_$during_conference_visits` times. Many of these visits were by the same
people. We know that the site was visited by `r c_$num_devices` unique devices,
but it is likely some of these devices are owned by the same people [^issue88].
Most of the visits were during conference hours. The hours of the conference,
along with the times of the conference events, are shown below.

[^issue88]: We are seeking to improve our Google Analytics integration. See [Issue #88](https://github.com/8thlight/thumbtrack/issues/88).

Key results:

* Visits were consistent across all three days of the conference.
* Low visits before the conference could indicate the need for better promotion.
* Low visits after conference hours could indicate the need to support Community Events.

```{r sessions, fig.width=8, fig.height=8}
sessions_per_hour_plot +
  { conference_day_type_plot + hour_type_plot } +
  plot_layout(nrow = 2)
```

# When did new users arrive at the site?

How did the railsconf.today spread among conference participants? If people were sharing the
app organically throughout the conference, we might see a pickup in new users throughout the
conference. Instead, what we see is that new users were "front loaded", meaning that most of
them knew about the app either before the conference or started using it in the first day.

```{r new-users}
new_users_plot
```

# What devices did people use to view the site?

This site was designed as a "mobile first" web application, but what percentage of users
used the app on a mobile device? During Rails Conf, `r c_$pct_mobile`% of users were on
mobile devices. The total numbers of mobile, desktop, and tablet devices are shown below.

Some of the styling on the site depends on a media query based on browser width. For future
uses of the site, we want to be able to ensure the best possible viewing experience by knowing
the typical viewing dimensions. During the conference, the smallest
mobile device view registered `r c_$min_browser_width` x `r c_$min_browser_height` pixels.
The distribution of browser widths by device is shown below.

```{r devices, fig.width=8}
devices_plot +
  browser_sizes_plot +
  plot_layout(widths = c(0.4, 0.6))
```

# How are people interacting with the site?

Users can interact with the app in a few ways. They can view the schedule for different days
of the conference. They can swipe to view the parallel events in a single timeslot, or dropdown
to see all the parallel events in a list. They can pin an event in a parallel timeslot that
they want to see. And they can click on outbound links to the official conference website,
or to 8th Light's website.

Users were most active in terms of events on the first day of the conference. Given that visits
to the site were consistent across all days of the conference, this suggests that many users
explored the site during their first few visits, viewing all the events, and pinning the ones
they wanted to go to. On subsequent days, users continued to use the site, but without interacting
with it as much, indicating that they were using it as their scheduler for the conference.

```{r events, fig.width=10}
events_plot
```

# Footnotes